What We Eval in the Shadows

### 2021-04-15 paper/main.tex
Example of assignment: sampling assigments for a MCM run

\mypara{Assigment \c{<-}.}

@@

\eval is a powerful tool and can be sometimes with functions with more specialized goals. For instance, variable lookup in any environment can be performed with \c{get}. Building a call and executing can be done with \c{do.call}. Nevertheless, \eval shines when expressions passed to it can be of many different types. % And it is shorter to type, and no need to remember all the specialized functions.

>>>>

\mypara{Assigments.} It corresponds to minimized expression \c{<-} and groups together \c{<-}, \c{<<-} and \c{assign}. Package \emph{plyr} has a function combine data frames by row, filling in missing columns. During the allocation of the missing columns, an assignment call is built with \c{assignment <- quote(column[rows] <<- what)} and later evaluated on demand in a setter function, with \c{eval(assigmment)}. Package \emph{overture} is used to run Markov Chain Monte Carlo. It runs an R expression repeatedly and saves any assignments that happen, as samples of the Markov chains. 
The expression is captured with \c{substitute} and a new environment \c{env} wrapping the parent of the caller is created, in which all assignments will happen. Regularly, the content of \c{env} is inspected to sample the assigned variables.
\begin{lstlisting}
function(expr, overwrite=over.write) {
	expr_q <- substitute(expr)
	env <- new.env(parent=parent.frame(1))
	samps <- list()
	RunMcmc(samps, 1, expr_q, env, n.save, backing.path, thin, exclude, overwrite)
}

RunMcmc <- function... {
	 ...
	 eval(expr_q, envir=env)
\end{lstlisting}

@@

\eval is a powerful tool and can be sometimes with functions with more specialized goals. For instance, variable lookup in any environment can be performed with \c{get}, and assignment in any environment, with \c{assign}. Building a call and executing can be done with \c{do.call}. Nevertheless, \eval shines when expressions passed to it can be of many different types. % And it is shorter to type, and no need to remember all the specialized functions.
